A Trio of 40 to 50 Million Year Old Mini-Neptunes from Kepler, TESS, and Gaia

### 2022-04-05 papers/ms.tex
update ms
Co-authored-by: Jason Curtis <jasonleecurtis@gmail.com>

% 208 words (250 max)
\begin{abstract}
  Stellar positions and velocities from Gaia are yielding a new and
  refined view of open cluster dispersal.
  Here we present an analysis of a group stars spanning Cepheus
  ($l=100^\circ$) to Hercules ($l=40^\circ$), hereafter the Cep-Her
  complex.
  The group includes four Kepler Objects of Interest:
  Kepler-1643 b ($R_{\rm p} = 2.32 \pm 0.14\,R_\oplus$, $P = 5.3\ {\rm days}$),
  KOI-7368 b ($R_{\rm p} = 2.22 \pm 0.12\,R_\oplus$, $P = 6.8\ {\rm days}$), 
  KOI-7913 Ab ($R_{\rm p} = 2.34 \pm 0.18\,R_\oplus$, $P = 24.2\ {\rm days}$), and
  Kepler-1627 Ab ($R_{\rm p} = 3.85 \pm 0.11\,R_\oplus$, $P = 7.2\ {\rm days}$).
  The latter Neptune-sized planet has previously been noted to be in
  the $\delta$\ Lyr\ cluster \citep{bouma_kep1627_2022}, which we
  argue here is a sub-component of the Cep-Her complex.
  Here we focus on the former three systems, which are in other
  sub-components of the complex.
  Based on kinematic evidence from Gaia, stellar rotation periods from
  TESS, and spectroscopy, these three systems are also $\approx$40
  million years old.
  More specifically, we find that Kepler-1643 is in a dense
  sub-cluster of the complex called RSG-5, and is $46^{+9}_{-7}$\,Myr old.
  KOI-7368 and KOI-7913 are in a diffuse region that we call
  CH-2, and are $36^{+10}_{-8}$\,Myr old.
  Based on the transit shapes and high resolution imaging, all three are
  most likely planets, with false positive probabilities of
  $6\times10^{-9}$, $4\times10^{-3}$, and $1\times10^{-4}$ for
  Kepler-1643, KOI-7368, and KOI-7913 respectively.
  These planets therefore empirically
  demonstrate that mini-Neptunes with sizes of $\approx$2 Earth
  radii exist at ages of $\approx$40 million years.
\end{abstract}

@@

An independent way to assess the age of the candidate cluster members
is to measure their stellar rotation periods.  This approach can be
achieved using surveys such as TESS \citep{ricker_transiting_2015} and
ZTF \citep{bellm_zwicky_2019}, and it leverages a storied tradition of
rotation period measurement for benchmark open clusters \citep[see
{\it e.g.},][]{skumanich_time_1972,curtis_rup147_2020}.  The TESS data
in our case are especially useful, since they provide 3 to 5 lunar
months of photometry for all of our candidate CH-2 and RSG-5 members.

We selected stars suitable for gyrochronology by requiring $\bpmrpo
\geq 0.5$ and $G<16$.  The latter cut corresponds to $\bpmrpo \lesssim
2.6$, at the relevant distances.  These cuts gave 19 stars in CH-2 and
42 stars in RSG-5.  We extracted light curves from the TESS images for
these stars using the \texttt{unpopular} package
\citep{hattorio_2021_cpm}, and regressed them against systematics with
its causal pixel model.  {\bf For the ZTF light curves, we used the
default photometry?  Ran aperture photometry on the image cutouts?}.
We then measured candidate rotation periods using a Lomb-Scargle
periodogram, and visually inspected them following the methods
discussed in \citet{curtis_rup147_2020}.

>>>>

% 208 words (250 max)
\begin{abstract}
  Stellar positions and velocities from Gaia are yielding a new and
  refined view of open cluster dispersal.
  Here we present an analysis of a group stars spanning Cepheus
  ($l=100^\circ$) to Hercules ($l=40^\circ$), hereafter the Cep-Her
  complex.
  The group includes four Kepler Objects of Interest:
  Kepler-1643 b ($R_{\rm p} = 2.32 \pm 0.14\,R_\oplus$, $P = 5.3\ {\rm days}$),
  KOI-7368 b ($R_{\rm p} = 2.22 \pm 0.12\,R_\oplus$, $P = 6.8\ {\rm days}$), 
  KOI-7913 Ab ($R_{\rm p} = 2.34 \pm 0.18\,R_\oplus$, $P = 24.2\ {\rm days}$), and
  Kepler-1627 Ab ($R_{\rm p} = 3.85 \pm 0.11\,R_\oplus$, $P = 7.2\ {\rm days}$).
  The latter Neptune-sized planet is in a sub-component of the
  Cep-Her complex called the $\delta$\ Lyr\ cluster
  \citep{bouma_kep1627_2022}.
  Here we focus on the former three systems, which are in other
  sub-components of the complex.
  Based on kinematic evidence from Gaia, stellar rotation periods from
  TESS, and spectroscopy, these three systems are also $\approx$40
  million years old.
  More specifically, we find that Kepler-1643 is in a dense
  sub-cluster of the complex called RSG-5, and is $46^{+9}_{-7}$\,Myr old.
  KOI-7368 and KOI-7913 are in a diffuse region that we call
  CH-2, and are $36^{+10}_{-8}$\,Myr old.
  Based on the transit shapes and high resolution imaging, all three are
  most likely planets, with false positive probabilities of
  $6\times10^{-9}$, $4\times10^{-3}$, and $1\times10^{-4}$ for
  Kepler-1643, KOI-7368, and KOI-7913 respectively.
  These planets therefore empirically
  demonstrate that mini-Neptunes with sizes of $\approx$2 Earth
  radii exist at ages of $\approx$40 million years.
\end{abstract}

@@

An independent way to assess the age of the candidate cluster members
is to measure their stellar rotation periods.  This approach can be
achieved using surveys such as TESS \citep{ricker_transiting_2015} and
the Zwicky Transient Facility (ZTF, \citealt{bellm_zwicky_2019}), and
it leverages a storied tradition of rotation period measurement for
benchmark open clusters \citep[see {\it
e.g.},][]{skumanich_time_1972,curtis_rup147_2020}.  The TESS data in
our case are especially useful, since they provide 3 to 5 lunar months
of photometry for all of our candidate CH-2 and RSG-5 members.

We selected stars suitable for gyrochronology by requiring $\bpmrpo
\geq 0.5$ to focus on FGKM stars that experience magnetic braking.
For TESS, we also restricted our sample to $G<16$, to ensure the stars
are bright enough to extract usable light curves from the full-frame
images (FFIs).  The magnitude cut corresponds to $\bpmrpo < 2.6$
($\sim$M3V) at the relevant distances.  These cuts gave 19 stars in
CH-2 and 42 stars in RSG-5.  We extracted light curves from the TESS
images for these stars using the \texttt{unpopular} package
\citep{hattorio_2021_cpm}, and regressed them against systematics with
its causal pixel model.  We measured rotation periods using
Lomb-Scargle periodograms and visually vetted the results using an
interactive program that allows us to switch between TESS Cycles,
select particular sectors, flag stars with multiple periods, and
correct half-period harmonics. For ZTF, we used the same color cut to
focus on FGKM stars, but restricted the sample to $13 < G < 18$ to
avoid the saturation limit on the bright end and ensure sufficient
photometric precision at the faint end. We followed the procedure
outlined in \citet{curtis_rup147_2020}: we downloaded $8'\times8'$
image cutouts, ran aperture photometry for the target and neighboring
stars identified with Gaia, and used them to define a systematics
correction to refine the target light curves. 
%Like for TESS, we also
%calculated periods with Lomb-Scargle periodograms using an interactive
%program that allows us to visually validate our measurements.
{\bf How many stars with periods from TESS? ZTF? Overlap?
Consistency? }
